Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-03-12 analysis/paper/paper.Rmd
flesh out examples section with Kamvar et al.

The fourth level includes packaging the analysis as a software package, *e.g.* R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder,<https://mybinder.org> can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, -@Miorini2019].

-   Example from Grünwald lab/Zhian:

    -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>/<https://github.com/zkamvar/Sudden_Oak_Death_in_Oregon_Forests>

>>>>

The fourth level includes packaging the analysis as a software package, *e.g.*, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done.
Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].
When this level is employed, tools such as Binder, <https://mybinder.org>, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, -@Miorini2019].
Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most ouptut files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.
